Lab News

### 2023-08-29 index.qmd
add news items and fix a description

<font color="#d08770">[June 28 2023].</font> **New award**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.

>>>>

<font color="#d08770">[August 28 2023].</font> **New members**. Welcome to Daniel Deletsu and Jiaqiao (Jack) Tang. Daniel will be starting his M.Sc in the lab and Jack will be starting his Ph.D in the lab.

<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.
